IMPC Mouse data - Variance in sex differences

### 2019-08-21 scripts/2019_July_IMPC variance and sex difference.Rmd
update

---
title: "IMPC Mouse data - Variance in sex differences"
author: "Susanne & Felix Zajitschek"
date: "July 2019"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
    toc_depth: 3
  html_notebook: 
    toc: yes
#runtime: shiny
---

@@

# Packages

@@

# Loading functions that are necessary
### Preparation of raw data
1) Data loading and cleaning of the csv file
This step we have already done and provide a cleaned up file which is less computing intensive. However, cvs
```{r}

@@

## Functions for preparing the data for meta analyses
3) "Population statistics"
```{r}
calculate_population_stats <- function(mydata, min_individuals = 5) {
  mydata %>% 
    group_by(population, strain_name, production_center, sex) %>% 
    summarise(
      trait = parameter_name[1],
      x_bar = mean(data_point),
      x_sd = sd(data_point),
      n_ind = n()
    ) %>% 
    ungroup() %>%
    filter(n_ind > min_individuals) %>% 
    # Check both sexes present & filter those missing
    group_by(population) %>% 
    mutate(
      n_sex = n_distinct(sex)
    ) %>% 
    ungroup() %>%
    filter(n_sex ==2) %>% 
    select(-n_sex) %>%
    arrange(production_center, strain_name, population, sex)
}
```

@@

We here provide the cleaned dataset, which we have saved in a folder called "export", as easy starting point. However, the full dataset can be loaded and cleaned using the data cleaning function (Function 1 above), if "#" signs in the code below are removed  (created as that is much smaller than the .csv - which we can still provide for those who absolutely want to start from scratch?)
```{r}
## Load raw data - save cleaned dataset as RDS for reuse
#data_raw <- load_raw("data/dr7.0_all_control_data.csv") %>%
#    clean_raw_data()
#dir.create("export", F, F)
#saveRDS(data_raw, "export/data_clean.rds")
getwd()
data1 <- readRDS("/export/data_clean.rds") 
#data1 
```

@@

## Preparation for Meta analysis
### Define population variable & add grouping variables

@@

 group <- read.csv("/export/ParameterGrouping.csv") 
 data <- data3
 data$parameterGroup <- group$parameter[match(data$parameter_name, group$parameter_name)]

@@

### Assign each unique parameter_name (=trait,use trait variable) a unique number ('id')
We add a new variable, where redundant traits are combined
[note however, at this stage the dataset still contains nonsensical traits, i.e. traits that may not contain any information on variance]

@@

### Create a matrix to store results for all traits
As the current version of this script utilizes a loop instead of tidyR code, it is here necessary to create an empty matrix, in which the returning values will be stored.

@@

## LOOP, to run meta-analysis on all traits
The loop combines the functions mentioned above and fills the data matrix with results from our meta analysis. 
Error messages indicate traits that either did not reach convergence, or that did not return meaningful results in the meta-analysis, due to absence of variance. Those traits will be removed in later steps, outlined below.

@@

```{r}
procedures <- read.csv("/export/procedures.csv")

@@

## Dealing with Correlated Parameters

@@

### Collapsing correlated parameters

@@

### Count of number of parameter names (correlated sub-traits) in each parameter group (par_group_size) 
This serves to identify and separate the traits that are correlated from the full dataset that can be processed as is. If the sample size (n) for a given "parameter group" equals 1, the trait is unique and uncorrelated. All instances, where there are 2 or more traits associated with the same  parameter group (90 cases), are selected for a "mini-meta analysis", which removes the issue of correlation.

@@

# Preparation for Visualization and Meta-analysis

@@

### Extract and save parameter estimates 
Function to collect the outcomes of the "mini" meta analysis
```{r}
count_fun <- function(mod_sub)
  return(c(mod_sub$reg_table$b.r, mod_sub$reg_table$CI.L, mod_sub$reg_table$CI.U, mod_sub$reg_table$SE))   #estimate, lower ci, upper ci, SE
```

@@

### Clean-up and rename 
```{r}
metacombo <-metacombo[, c(1, 21:23, 2:13)] 
names(metacombo)[3] <- "procedure" 
names(metacombo)[4] <- "GroupingTerm"

@@

trait_meta_results <- write.csv(metacombo, file = "/export/trait_meta_results.csv")
```

## Last step: meta-meta-analysis 
### Perform meta-analyses (3 for each of the 9 grouping terms: lnCVR, lnVR, lnRR) 
This is the full result dataset
```{r}

@@

### Prepare data
Nesting, calculating the number of parameters within each grouping term, and running the meta-analysis
```{r}
metacombo_final <- metacombo %>%
 group_by(GroupingTerm) %>%
 nest()

@@

# PLOTS

## Plot FIGURE 2 (First-order meta analysis results)

@@

### Prepare data for traits with CI not overlapping 0
create column with 1= different from zero, 0= zero included in CI
```{r}

@@

```
### Create final combined Figure (Figure 2)
```{r}

Fig2 <- ggarrange(malebias_Fig2_alltraits, malebias_Fig2_sigtraits,malebias_Fig2_over10, nrow = 3, align = "v", heights = c(1.22,1,1))
Fig2
#ggsave("Fig2.pdf", plot = Fig2, width = 6, height = 5) 
```

## Preparation, for Figure 3: Overall results of second order meta anlaysis
### Restructure data for plotting 
Data are restructured, and grouping terms are being re-ordered
```{r}
overall3 <- gather(overall2, parameter, value, c(lnCVR, lnVR, lnRR), factor_key= TRUE)

@@

### Plot FIGURE 3 (Second-order meta analysis results)

@@

### Prepare data for traits with CI not overlapping 0

@@

#######################
### Female Figure
Female Fig3 sig

@@

### Plot Fig3 all significant results (CI not overlapping zero, female )
```{r}

@@

### Fig3 >10%

@@

### Male Fig 3 > 10% (male biased traits)
```{r}
meta.male.plot3.perc <- metacombo %>% 
    	mutate(percCVR = ifelse(lnCVR > log (11/10), 1, 0),			
	percVR = ifelse(lnVR > log (11/10), 1, 0),
	percRR = ifelse(lnRR > log (11/10), 1, 0))

@@

plot3.male.meta.RR.perc.b <- as.data.frame(plot3.male.meta.RR.perc %>% group_by(GroupingTerm) %>%  
	mutate(lnRR = map_dbl(model_lnRR, pluck(2)), lnRR_lower = map_dbl(model_lnRR, pluck(6)), 
	lnRR_upper =map_dbl(model_lnRR, pluck(7)), lnRR_se =map_dbl(model_lnRR, pluck(3))) )[, c(1,4:7)] 
add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.male.meta.RR.perc.b))
plot3.male.meta.RR.perc.b <- rbind(plot3.male.meta.RR.perc.b, add.row.hearing) 
plot3.male.meta.RR.perc.b <- plot3.male.meta.RR.perc.b[order(plot3.male.meta.RR.perc.b$GroupingTerm),]

@@

Metameta_Fig3_male.perc <- overall4.male.perc %>% filter(., GroupingTerm != "Hearing") %>%
  ggplot(aes(y= GroupingTerm, x= value)) +
  geom_errorbarh(aes(xmin = ci.low, 
                     xmax = ci.high), 
			   height = 0.1, show.legend = FALSE) +
  geom_point(aes(shape = parameter,
             fill = parameter), color = 'mediumaquamarine', size = 2.2, 
             show.legend = FALSE) +
  scale_x_continuous(limits=c(-0.2, 0.62), 
                     breaks = c(0, 0.3), 
                     name='Effect size') +
  geom_vline(xintercept=0, 
             color='black', 
             linetype='dashed')+
  facet_grid(cols = vars(parameter), rows = vars(label),
             labeller = label_wrap_gen(width = 23),
             scales= 'free', 
             space='free')+
  theme_bw()+
  theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
	  strip.text.x = element_blank(),
        strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
        text = element_text(size = 14),
        panel.spacing = unit(0.5, "lines"),
        panel.border= element_blank(),
        axis.line=element_line(), 
        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.title = element_blank(),
        axis.title.x = element_text(hjust = 0.5, size = 14),
	  axis.title.y = element_blank())

@@

plot3.meta.RR.perc.b <- as.data.frame(plot3.meta.RR.perc %>% group_by(GroupingTerm) %>%  
	mutate(lnRR = map_dbl(model_lnRR, pluck(2)), lnRR_lower = map_dbl(model_lnRR, pluck(6)), 
	lnRR_upper =map_dbl(model_lnRR, pluck(7)), lnRR_se =map_dbl(model_lnRR, pluck(3))) )[, c(1,4:7)] 
add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.meta.RR.perc.b))
plot3.meta.RR.perc.b <- rbind(plot3.meta.RR.perc.b, add.row.hearing) 
plot3.meta.RR.perc.b <- plot3.meta.RR.perc.b[order(plot3.meta.RR.perc.b$GroupingTerm),]

@@

### Restructure data for plotting
Female bias, 10 percent difference
```{r}
overall3.perc <- gather(overall.plot3.perc, parameter, value, c(lnCVR, lnVR, lnRR), factor_key= TRUE)

@@

# Plot Fig3 all plots combined
```{r}
library(ggpubr)
Fig3.bottom <- ggarrange(Metameta_Fig3_female.sig, Metameta_Fig3_male.sig, Metameta_Fig3_female.perc, Metameta_Fig3_male.perc, 
		   ncol = 2, nrow = 2, widths = c(1, 1.20), heights = c(1, 1))

@@

# Heterogeneity
## FIGURE 4 (Second-order meta analysis on heterogeneity)
### Create matrix to store results for all traits
```{r}
results.allhetero.grouping <- as.data.frame(cbind(c(1:n), matrix(rep(0, n*30), ncol = 30))) 
names(results.allhetero.grouping) <- c("id", "sigma2_strain.CVR", "sigma2_center.CVR", "sigma2_error.CVR", "s.nlevels.strain.CVR", 
	"s.nlevels.center.CVR", "s.nlevels.error.CVR", "sigma2_strain.VR", "sigma2_center.VR", "sigma2_error.VR", "s.nlevels.strain.VR", 
	"s.nlevels.center.VR", "s.nlevels.error.VR", "sigma2_strain.RR", "sigma2_center.RR", "sigma2_error.RR", "s.nlevels.strain.RR", 
	"s.nlevels.center.RR", "s.nlevels.error.RR", "lnCVR", "lnCVR_lower", "lnCVR_upper", "lnCVR_se", "lnVR", "lnVR_lower", "lnVR_upper", 
	"lnVR_se", "lnRR", "lnRR_lower", "lnRR_upper" ,"lnRR_se")

@@

## LOOP
parameters to extract from metafor (sigma2's, s.nlevels)

@@

@@

### Exclude traits
```{r}
results.allhetero.grouping2 <- results.allhetero.grouping[results.allhetero.grouping$s.nlevels.strain.VR != 0, ]
nrow(results.allhetero.grouping2) #218
```

Merge data sets containing metafor results with procedure etc. names 
```{r}
#procedures <- read.csv("procedures.csv")

@@

### Dealing with correlated parameters
```{r}
metahetero1 <- results.allhetero.grouping2 
length(unique(metahetero1$procedure)) #18
length(unique(metahetero1$GroupingTerm)) #9 
length(unique(metahetero1$parameter_group)) # 149 levels: one more tha in effect size alanlysis, see above; CHECK!
length(unique(metahetero1$parameter_name)) #218

@@

## **Extract and save parameter estimates 
```{r}
count_fun. <- function(mod_sub)
  return(c(as.numeric(mod_sub$mod_info$term1), mod_sub$N) )

@@

robu_all. <- full_join(robusub_CVR., robusub_VR.) %>% full_join(., robusub_RR.)

### **Merge the two data sets (the new [robu_all] and the initial [uncorrelated sub-traits with count = 1]) 
  In this step, we 	
1) put the N from robumeta and the  N from metafor (s.nlevels.error) together into the same columns (N.RR, N.VR, N.CVR)

2) calculate the total variance for metafor models as the sum of random effect variances and the residual error,
							then put them in the same columns together with the residual variances from robumeta
```{r}
metahetero_all <- metahetero1 %>% filter(par_group_size == 1) %>% as_tibble
metahetero_all$N.RR <- metahetero_all$s.nlevels.error.RR 
metahetero_all$N.CVR <- metahetero_all$s.nlevels.error.CVR 
metahetero_all$N.VR <- metahetero_all$s.nlevels.error.VR

# log (srt( of the data to look at))
metahetero_all$var.RR <- log(sqrt(metahetero_all$sigma2_strain.RR + metahetero_all$sigma2_center.RR + metahetero_all$sigma2_error.RR))
metahetero_all$var.VR <- log(sqrt(metahetero_all$sigma2_strain.VR + metahetero_all$sigma2_center.VR + metahetero_all$sigma2_error.VR))
metahetero_all$var.CVR <- log(sqrt(metahetero_all$sigma2_strain.CVR + metahetero_all$sigma2_center.CVR + metahetero_all$sigma2_error.CVR))
#str(metahetero_all)
#str(robu_all.)

#adjust the -inf to smallest number in dataset
metahetero_all <- metahetero_all %>% mutate(var.RR = if_else(var.RR == -Inf, -7 ,var.RR),
                   	  var.VR = if_else(var.VR == -Inf, -5 ,var.VR),
				  var.CVR = if_else(var.CVR == -Inf, -6 ,var.CVR))

# **Combine data 
# Step1

combinedmetahetero <- bind_rows(robu_all., metahetero_all)
#glimpse(combinedmetahetero)

@@

metacombohetero <- metacombohetero[, c(1:7, 43:45)] 
names(metacombohetero)[9] <- "procedure" 
names(metacombohetero)[10] <- "GroupingTerm"

#write.csv(metacombohetero, "metacombohetero.csv")

## *Last step: meta-meta-analysis of heterogeneity
```{r}
#glimpse(metacombohetero)

## *Perform meta-meta-analysis (3 for each of the 9 grouping terms: var.CVR, var.VR, var.RR)

@@

# **Calculate number of parameters per grouping term : not needed; delete in final version
#metacombo_final <- metacombo_final  %>%  mutate(para_per_GroupingTerm = map_dbl(data, nrow))

# **Final fixed effects meta-analyses within grouping terms, with SE of the estimate 
# Shinichi: meta-analyses on heterogeneity, using  sei as below, in metafor formula

@@

heterog2 <- bind_rows(Behaviour., Morphology., Metabolism., Physiology., Immunology., Hematology., Heart., Hearing., Eye.)
#str(heterog2)

####################################################################################################################################
## Heterogeneity PLOTS

Restructure data for plotting 
```{r}
heterog3 <- gather(heterog2, parameter, value, c(heteroCVR, heteroVR, heteroRR), factor_key= TRUE)

@@

## *Plot FIGURE 4 (Second-order meta analysis on heterogeneity)

>>>>

---
title: "IMPC Mouse data - Variance in sex differences"
author: "Susanne & Felix Zajitschek"
date: "August 2019"
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_depth: 4
    toc_float: yes
  html_notebook:
    toc: yes
  pdf_document:
    toc: yes
    toc_depth: '4'
---

@@

## Set up
### Packages

@@

### Loading functions that are necessary
#### Preparation of raw data
1) Data loading and cleaning of the csv file
This step we have already done and provide a cleaned up file which is less computing intensive. However, cvs
```{r}

@@

#### Functions for preparing the data for meta analyses
3) "Population statistics"
```{r}
calculate_population_stats <- function(mydata, min_individuals = 5) {
  mydata %>% 
    group_by(population, strain_name, production_center, sex) %>% 
    summarise(
      trait = parameter_name[1],
      x_bar = mean(data_point),
      x_sd = sd(data_point),
      n_ind = n()
    ) %>% 
    ungroup() %>%
    filter(n_ind > min_individuals) %>% 
    # Check both sexes present & filter those missing
    group_by(population) %>% 
    mutate(
      n_sex = n_distinct(sex)
    ) %>% 
    ungroup() %>%
    filter(n_sex ==2) %>% 
    select(-n_sex) %>%
    arrange(production_center, strain_name, population, sex)
}
```

@@

We here provide the cleaned dataset, which we have saved in a folder called "export", as easy starting point. However, the full dataset can be loaded and cleaned using the data cleaning function (Function 1 above), if "#" signs in the code below are removed  (created as that is much smaller than the .csv - which we can still provide for those who absolutely want to start from scratch?)
```{r}
## Load raw data - save cleaned dataset as RDS for reuse
#data_raw <- load_raw("data/dr7.0_all_control_data.csv") %>%
#    clean_raw_data()
#dir.create("export", F, F)
#saveRDS(data_raw, "export/data_clean.rds")
getwd()
data1 <- readRDS("../export/data_clean.rds") 
#data1 
```

@@

## Meta analysis, Phase 1
### Preparation
#### Define population variable & add grouping variables

@@

 group <- read.csv("../export/ParameterGrouping.csv") 
 data <- data3
 data$parameterGroup <- group$parameter[match(data$parameter_name, group$parameter_name)]

@@

#### Assign each unique parameter_name (=trait,use trait variable) a unique number ('id')
We add a new variable, where redundant traits are combined
[note however, at this stage the dataset still contains nonsensical traits, i.e. traits that may not contain any information on variance]

@@

#### Create a matrix to store results for all traits
As the current version of this script utilizes a loop instead of tidyR code, it is here necessary to create an empty matrix, in which the returning values will be stored.

@@

### LOOP, to run meta-analysis on all traits
The loop combines the functions mentioned above and fills the data matrix with results from our meta analysis. 
Error messages indicate traits that either did not reach convergence, or that did not return meaningful results in the meta-analysis, due to absence of variance. Those traits will be removed in later steps, outlined below.

@@

```{r}
procedures <- read.csv("../export/procedures.csv")

@@

## Meta-analysis, Phase 2
### Dealing with Correlated Parameters, preparation

@@

#### Collapsing and merging correlated parameters

@@

#### Count of number of parameter names (correlated sub-traits) in each parameter group (par_group_size) 
This serves to identify and separate the traits that are correlated from the full dataset that can be processed as is. If the sample size (n) for a given "parameter group" equals 1, the trait is unique and uncorrelated. All instances, where there are 2 or more traits associated with the same  parameter group (90 cases), are selected for a "mini-meta analysis", which removes the issue of correlation.

@@

@@

#### Extract and save parameter estimates 
Function to collect the outcomes of the "mini" meta analysis
```{r}
count_fun <- function(mod_sub)
  return(c(mod_sub$reg_table$b.r, mod_sub$reg_table$CI.L, mod_sub$reg_table$CI.U, mod_sub$reg_table$SE))   #estimate, lower ci, upper ci, SE
```

@@

#### Clean-up and rename 
```{r}
metacombo <-metacombo[, c(1, 21:23, 2:13)] 
names(metacombo)[3] <- "procedure" 
names(metacombo)[4] <- "GroupingTerm"

@@

#trait_meta_results <- write.csv(metacombo, file = "export/trait_meta_results.csv")
```

## Meta-analysis, Phase 3
#### Perform meta-analyses (3 for each of the 9 grouping terms: lnCVR, lnVR, lnRR) 
This is the full result dataset
```{r}

@@

#### Prepare data
Nesting, calculating the number of parameters within each grouping term, and running the meta-analysis
```{r}
metacombo_final <- metacombo %>%
 group_by(GroupingTerm) %>%
 nest()

@@

### Visualisation

#### Plot FIGURE 2 [4 in ms] (First-order meta analysis results)

@@

#### Prepare data for traits with CI not overlapping 0
create column with 1= different from zero, 0= zero included in CI
```{r}

@@

```
#### Create final combined Figure (Figure 2)
```{r}

Fig2 <- ggarrange(malebias_Fig2_alltraits, malebias_Fig2_sigtraits,malebias_Fig2_over10, nrow = 3, align = "v", heights = c(1.22,1,1), labels = c("A", "B", "C"))
Fig2
ggsave("Fig2.pdf", plot = Fig2, width = 6, height = 5) 
```

###  Overall results of second order meta anlaysis (Figure 4a)
#### Restructure data for plotting 
Data are restructured, and grouping terms are being re-ordered
```{r}
overall3 <- gather(overall2, parameter, value, c(lnCVR, lnVR, lnRR), factor_key= TRUE)

@@

#### Plot FIGURE 4 (Second-order meta analysis results)

@@

#### Figure 4B:  Prepare data for traits with CI not overlapping 0

@@

#######################
#### Female Figure, significant traits
Female Fig3 sig

@@

Plot Fig3 all significant results (CI not overlapping zero, female )
```{r}

@@

#### Fig4 C >10%

@@

#### Male Fig 3 > 10% (male biased traits)
```{r}
meta.male.plot3.perc <- metacombo %>% 
    	mutate(percCVR = ifelse(lnCVR > log (11/10), 1, 0),			
	percVR = ifelse(lnVR > log (11/10), 1, 0),
	percRR = ifelse(lnRR > log (11/10), 1, 0))

@@

plot3.male.meta.RR.perc.b <- as.data.frame(plot3.male.meta.RR.perc %>% group_by(GroupingTerm) %>%  
	mutate(lnRR = map_dbl(model_lnRR, pluck(2)), lnRR_lower = map_dbl(model_lnRR, pluck(6)), 
	lnRR_upper =map_dbl(model_lnRR, pluck(7)), lnRR_se =map_dbl(model_lnRR, pluck(3))) )[, c(1,4:7)] 
add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% 
  setNames(names(plot3.male.meta.RR.perc.b))
plot3.male.meta.RR.perc.b <- rbind(plot3.male.meta.RR.perc.b, add.row.hearing)

add.row.eye <- as.data.frame(t(c("Eye", NA, NA, NA, NA))) %>% 
  setNames(names(plot3.male.meta.RR.perc.b))
plot3.male.meta.RR.perc.b <- rbind(plot3.male.meta.RR.perc.b, add.row.eye)

plot3.male.meta.RR.perc.b <- plot3.male.meta.RR.perc.b[order(plot3.male.meta.RR.perc.b$GroupingTerm),]

@@

Metameta_Fig3_male.perc <- overall4.male.perc %>% #filter(., GroupingTerm != "Hearing") %>%
  ggplot(aes(y= GroupingTerm, x= value)) +
  geom_errorbarh(aes(xmin = ci.low, 
                     xmax = ci.high), 
			   height = 0.1, show.legend = FALSE) +
  geom_point(aes(shape = parameter,
             fill = parameter), color = 'mediumaquamarine', size = 2.2, 
             show.legend = FALSE) +
  scale_x_continuous(limits=c(-0.2, 0.62), 
                     breaks = c(0, 0.3), 
                     name='Effect size') +
  geom_vline(xintercept=0, 
             color='black', 
             linetype='dashed')+
  facet_grid(cols = vars(parameter), rows = vars(label),
             labeller = label_wrap_gen(width = 23),
             scales= 'free', 
             space='free')+
  theme_bw()+
  theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
	  strip.text.x = element_blank(),
        strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
        text = element_text(size = 14),
        panel.spacing = unit(0.5, "lines"),
        panel.border= element_blank(),
        axis.line=element_line(), 
        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.title = element_blank(),
        axis.title.x = element_text(hjust = 0.5, size = 14),
	  axis.title.y = element_blank())

@@

plot3.meta.RR.perc.b <- as.data.frame(plot3.meta.RR.perc %>% group_by(GroupingTerm) %>%  
	mutate(lnRR = map_dbl(model_lnRR, pluck(2)), lnRR_lower = map_dbl(model_lnRR, pluck(6)), 
	lnRR_upper =map_dbl(model_lnRR, pluck(7)), lnRR_se =map_dbl(model_lnRR, pluck(3))) )[, c(1,4:7)] 
add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.meta.RR.perc.b))
plot3.meta.RR.perc.b <- rbind(plot3.meta.RR.perc.b, add.row.hearing) 
add.row.hematology <- as.data.frame(t(c("Hematology", NA, NA, NA, NA))) %>% 
  setNames(names(plot3.meta.RR.perc.b))
plot3.meta.RR.perc.b <- rbind(plot3.meta.RR.perc.b, add.row.hematology)

plot3.meta.RR.perc.b <- plot3.meta.RR.perc.b[order(plot3.meta.RR.perc.b$GroupingTerm),]

@@

#### Restructure data for plotting
Female bias, 10 percent difference
```{r}
overall3.perc <- gather(overall.plot3.perc, parameter, value, c(lnCVR, lnVR, lnRR), factor_key= TRUE)

@@

#### Plot Fig3 all plots combined
```{r}
library(ggpubr)
Fig3.bottom <- ggarrange(Metameta_Fig3_female.sig, Metameta_Fig3_male.sig, Metameta_Fig3_female.perc, Metameta_Fig3_male.perc, 
		   ncol = 2, nrow = 2, widths = c(1, 1.20), heights = c(1, 1))

@@

### Heterogeneity
#### FIGURE 4 (Second-order meta analysis on heterogeneity)
#### Create matrix to store results for all traits
```{r}
results.allhetero.grouping <- as.data.frame(cbind(c(1:n), matrix(rep(0, n*30), ncol = 30))) 
names(results.allhetero.grouping) <- c("id", "sigma2_strain.CVR", "sigma2_center.CVR", "sigma2_error.CVR", "s.nlevels.strain.CVR", 
	"s.nlevels.center.CVR", "s.nlevels.error.CVR", "sigma2_strain.VR", "sigma2_center.VR", "sigma2_error.VR", "s.nlevels.strain.VR", 
	"s.nlevels.center.VR", "s.nlevels.error.VR", "sigma2_strain.RR", "sigma2_center.RR", "sigma2_error.RR", "s.nlevels.strain.RR", 
	"s.nlevels.center.RR", "s.nlevels.error.RR", "lnCVR", "lnCVR_lower", "lnCVR_upper", "lnCVR_se", "lnVR", "lnVR_lower", "lnVR_upper", 
	"lnVR_se", "lnRR", "lnRR_lower", "lnRR_upper" ,"lnRR_se")

@@

#### LOOP
Parameters to extract from metafor (sigma2's, s.nlevels)

@@

for(t in 1:n) {
  tryCatch({

@@

#### Exclude traits
```{r}
results.allhetero.grouping2 <- results.allhetero.grouping[results.allhetero.grouping$s.nlevels.strain.VR != 0, ]
nrow(results.allhetero.grouping2) #218
```

Merge data sets containing metafor results with procedure etc. names 
```{r}
#procedures <- read.csv("../procedures.csv")

@@

#### Dealing with correlated parameters
```{r}
metahetero1 <- results.allhetero.grouping2 
length(unique(metahetero1$procedure)) #18
length(unique(metahetero1$GroupingTerm)) #9 
length(unique(metahetero1$parameter_group)) # 149 levels: one more tha in effect size alanlysis, see above; CHECK!
length(unique(metahetero1$parameter_name)) #218

@@

## **Extract and save parameter estimates

count_fun. <- function(mod_sub)
  return(c(as.numeric(mod_sub$mod_info$term1), mod_sub$N) )

@@

robu_all. <- full_join(robusub_CVR., robusub_VR.) %>% full_join(., robusub_RR.)
```

#### Merge the two data sets (the new [robu_all.] and the initial [uncorrelated sub-traits with count = 1])
In this step, we 	
1) merge the N from robumeta and the  N from metafor (s.nlevels.error) together into the same columns (N.RR, N.VR, N.CVR)
2) calculate the total variance for metafor models as the sum of random effect variances and the residual error, then add in the same columns together with the residual variances from robumeta
```{r}
metahetero_all <- metahetero1 %>% filter(par_group_size == 1) %>% as_tibble
metahetero_all$N.RR <- metahetero_all$s.nlevels.error.RR 
metahetero_all$N.CVR <- metahetero_all$s.nlevels.error.CVR 
metahetero_all$N.VR <- metahetero_all$s.nlevels.error.VR 
metahetero_all$var.RR <- log(sqrt(metahetero_all$sigma2_strain.RR + metahetero_all$sigma2_center.RR + metahetero_all$sigma2_error.RR))
metahetero_all$var.VR <- log(sqrt(metahetero_all$sigma2_strain.VR + metahetero_all$sigma2_center.VR + metahetero_all$sigma2_error.VR))
metahetero_all$var.CVR <- log(sqrt(metahetero_all$sigma2_strain.CVR + metahetero_all$sigma2_center.CVR + metahetero_all$sigma2_error.CVR))
#str(metahetero_all)
#str(robu_all.)

metahetero_all <- metahetero_all %>% mutate(var.RR = if_else(var.RR == -Inf, -7 ,var.RR),
                   	  var.VR = if_else(var.VR == -Inf, -5 ,var.VR),
				  var.CVR = if_else(var.CVR == -Inf, -6 ,var.CVR))

# **Combine data 
## Step1 
combinedmetahetero <- bind_rows(robu_all., metahetero_all)
#glimpse(combinedmetahetero)

@@

metacombohetero <- metacombohetero[, c(1:7, 43:45)] 
names(metacombohetero)[9] <- "procedure" 
names(metacombohetero)[10] <- "GroupingTerm" 
```

#### Last step: meta-meta-analysis of heterogeneity
```{r}
## *Perform meta-meta-analysis (3 for each of the 9 grouping terms: var.CVR, var.VR, var.RR)

@@

metacombohetero$var.CVR

@@

heterog2 <- bind_rows(Behaviour., Morphology., Metabolism., Physiology., Immunology., Hematology., Heart., Hearing., Eye.)
#str(heterog2)
```

#### Heterogeneity PLOTS
Restructure data for plotting 
```{r}
heterog3 <- gather(heterog2, parameter, value, c(heteroCVR, heteroVR, heteroRR), factor_key= TRUE)

@@

#### Plot FIGURE 4 (5 in ms) (Second-order meta analysis on heterogeneity)
